Spin canonical divisors of log stacky curves

### 2015-06-29 stacky_write_up/spin_cring.tex
remove fractional weight corollary

\begin{thm}
\label{thm:main}
Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect field $k$, \todo{Ask David: do we need this perfectness assumption everywhere?} so
that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$. Then the
canonical ring

@@

Lemma \ref{lem:sat-1} leads to the the following corollaries.
\todo{do we want this here?}
\begin{cor}\label{cor-gen-0-with-log}
If $(\sx, \halfcan, \Delta)$ is a stacky curve with signature $(g; e_1, \ldots, e_n; \delta)$ with $g=0$ and $\delta>0$, then $R_\halfcan$ is generated in degree at most $e=\max(e_i)$ with relations generated in degree at most $2e$.
\end{cor}
\begin{proof}
By remark \ref{rem:delta-not-1}, $\delta\ge 2$ so $\halfcan$ is linearly equivalent to an effective divisor.  Thus, we can recursively apply Lemma \ref{lem:sat-1} to prove the corollary.
\end{proof}

\todo{Something about fractional weight modular forms?}

\begin{cor}
Let $R_\halfcan$ be the fractional weight canonical ring associated to a fractional $\frac{2\alpha}{\beta}$-weight cusp forms with $\frac{\alpha}{\beta}$ in reduced form and $\beta\ge 3$, with signature $(g; e_1, \ldots, e_n; \delta)$ where $g=0$.  Then $R_\halfcan$ is generated in degrees at most $e = \max(e_i)$ with relations generated in degrees at most $2e$.
\end{cor}
\begin{proof}
Let $K$ be the log canonical divisor of the curve $(\sx, \Delta)$ associated to the $\frac{2\alpha}{\beta}$ weight cusp forms.  We see that $\frac{\beta}{\alpha}\halfcan_\sx\sim K_\sx$, so the floors of each

Then $\beta \halfcan_\sx \sim \alpha K_{\sx}$ so $\beta\lfloor$ so $\beta | \alpha \deg(K_\sx)$; since $\gcd(\alpha, \beta)=1$, $\beta| \deg(K_\sx)\ge -2$.  Thus, since $\beta\ge 3$, $\deg(K_\sx)\ge 0$.  Thus $\deg($
\end{proof}

>>>>

\todo{State for even weight modular forms attributed to VZB.}
\begin{thm}
\label{thm:main}
Let $(\sx, \Delta, \halfcan)$ be a log spin curve over a perfect field $k$, \todo{Ask David: do we need this perfectness assumption everywhere?} so
that $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r; \delta)$. Then the
canonical ring

@@

\iffalse{
Lemma \ref{lem:sat-1} leads to the the following corollaries.
\todo{do we want this here?}
\begin{cor}\label{cor-gen-0-with-log}
If $(\sx, \halfcan, \Delta)$ is a stacky curve with signature $(g; e_1, \ldots, e_n; \delta)$ with $g=0$ and $\delta>0$, then $R_\halfcan$ is generated in degree at most $e=\max(e_i)$ with relations generated in degree at most $2e$.
\end{cor}
\begin{proof}
By remark \ref{rem:delta-not-1}, $\delta\ge 2$ so $\halfcan$ is linearly equivalent to an effective divisor.  Thus, we can recursively apply Lemma \ref{lem:sat-1} to prove the corollary.
\end{proof}
}\fi
